---
title: "Examples"
output:
  github_document: default
  html_document: default
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  # dev = "pdf",
  # fig.ext = "pdf",
  fig.width = 5,
  fig.height = 3.5
)
```

```{r, message=FALSE}
source("functions.R")
```

#### Examples from Table 2

##### Example 2.8 

```{r plotQC}
k = 3
n = 4

f = generate_forecasts(k,n)

sle_DC = construct_sle_DC(k,n,f)

g_hom = solve_hom(sle_DC)
g_part = sle_DC$f

c = c(0.4,0.4,0.4)
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

fractions(t(g/n))

test_all(k,n,f,g)

plot_QC(k,n,f,g)
```

The figure plots upper and lower coverage (top) and predicted quantiles against quantile levels to facilitate visual verification of the quantile calibration condition.

##### Example 2.9

```{r plotUQC2.9}
k = 3
n = 4

f = generate_forecasts(k,n)[,c(1,1,1,2,3)]
g = matrix(c(0.5,0.4,0.1,
             0.1,0.2,0.7,
             0.4,0.1,0.5),nrow = 3)[,c(1,1,1,2,3)] * n

sle_TC = construct_sle_TC(k,n,f)

TC = test_sle(sle_TC,g)

cbind(test_all(k,n,f,g),TC)

plot_UQC(k,n,f,g)
```

#### Examples from Table 3

##### Example 3.3 (w = 0)

```{r plotUQC3.3}
k = 3
n = 4

f = generate_forecasts(k,n)

sle_DC = construct_sle_DC(k,n,f)

g_part = sle_DC$f
g_hom = solve_hom(sle_DC)

c = -c(2,0,0)
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

DC = test_sle(sle_DC,g)

cbind(test_all(k,n,f,g),DC)

plot_UQC(k,n,f,g)
```

The example is not unconditionally quantile calibrated because the upper coverage is not above the diagonal, e.g., $\mathbb{Q}(Y < F^{-1}(0.24)) = 1/6 < 0.24$.

##### Example 3.4: See below.

#### Examples from Table 4

##### Example: Vaicenavicius et al. (2019, Table 1)

```{r}
k = 3
n = 10

f = matrix(c(0.1,0.3,0.6,
             0.1,0.6,0.3,
             0.3,0.1,0.6,
             0.3,0.6,0.1,
             0.6,0.1,0.3,
             0.6,0.3,0.1),nrow = 3) * n
g = matrix(c(0.2,0.2,0.6,
             0.0,0.7,0.3,
             0.2,0.2,0.6,
             0.4,0.5,0.1,
             0.7,0.0,0.3,
             0.5,0.4,0.1),nrow = 3) * n

test_all(k,n,f,g)
```

##### Example: Vaicenavicius et al. (2019, Supplement, Table 2)

```{r}
k = 3
n = 10
f = matrix(c(0.6,0.1,0.3,
             0.4,0.6,0.0),nrow = 3) * n
g = matrix(c(0.7,0.2,0.1,
             0.3,0.5,0.2),nrow = 3) * n

test_all(k,n,f,g)
```

##### Example: Silva Filho et al. (2023, Footnote 2)

```{r}
k = 3
n = 10
f = matrix(c(0.3,0.3,0.4,
             0.4,0.3,0.3,
             0.4,0.6,0.0,
             0.3,0.6,0.1),nrow = k) * n
g = matrix(c(0.4,0.2,0.4,
             0.3,0.4,0.3,
             0.5,0.5,0.0,
             0.2,0.7,0.1),nrow = k) * n

test_all(k,n,f,g)
```

##### Example: Gneiting and Resin (2023, Example 2.4 (b))
For an illustrative analysis, see 'illustration.[Rmd/html]'.

```{r}
k = 3
n = 4

f = generate_forecasts(k,n)

sle_MC = construct_sle_MC(k,n,f)
sle_PC = construct_sle_PC(k,n,f)

sle = combine_sle(sle_MC,sle_PC)

g_part = sle$f
g_hom = solve_hom(sle)

c = -0.6 # in [-1,1] for (multiples of) probabilities
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

test_all(k,n,f,g)
```

##### Example: Gneiting and Resin (2023, Example 2.14 (b))

```{r}
k = 3
n = 4
f = generate_forecasts(k,n)

sle_TC = construct_sle_TC(k,n,f)

g_part = sle_TC$f
g_hom = solve_hom(sle_TC)

c = c(-0.6,0.6)
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)
# g = matrix(c(0.5,0.4,0.1,
#              0.1,0.5,0.4,
#              0.4,0.1,0.5),nrow = 3) * n

test_all(k,n,f,g)
```

##### Example 3.3 (w = 0.5)

```{r}
# Construct example with 3 classes (w = 0)
k = 3
n = 4

f = generate_forecasts(k,n)

sle_DC = construct_sle_DC(k,n,f)

g_part = sle_DC$f
g_hom = solve_hom(sle_DC)

c = -c(2,0,0)
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

# Add fourth class with probability w = 0.5 = 4/8 and rescale other probabilities
# by doubling n
k = 4
n = 8

f = rbind(f, c(4,4,4))
g = rbind(g, c(4,4,4))

sle_DC = construct_sle_DC(k,n,f)
DC = test_sle(sle_DC,g)

cbind(test_all(k,n,f,g),DC)

# plot_UQC(k,n,f,g)
```

##### Example 3.4

```{r}
k = 3
n = 5

f = generate_forecasts(k,n)

sle_fCC = construct_sle_fCC(k,n,f)

g_part = sle_fCC$f
g_hom = solve_hom(sle_fCC)

c =  1
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

sle_DC = construct_sle_DC(k,n,f)
DC = test_sle(sle_DC,g)

cbind(test_all(k,n,f,g),DC)
```
Note: As the example satisfies CC, it also satisfies QC in Table 3.

##### Example 3.14

```{r}
k = 4
n = 5

f = generate_forecasts(k,n)

sle_CwC = construct_sle_CwC(k,n,f)

g_part = sle_CwC$f
g_hom = solve_hom(sle_CwC)

c = c(-0.5,-0.5,-0.5,1,1)
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

test_all(k,n,f,g)
```

##### Example 3.15

```{r}
k = 3
n = 4

f = generate_forecasts(k,n)

sle_PC = construct_sle_PC(k,n,f)
sle_aPC = construct_sle_aPC(k,n,f)
sle = combine_sle(sle_PC,sle_aPC)

g_part = sle_PC$f
g_hom = solve_hom(sle)

c = c(2/3,2/3)
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

test_all(k,n,f,g)
```

##### Example 3.16

```{r}
k = 3
n = 6

f = generate_forecasts(k,n)[,-c(3,4,5,6)]

sle_fPC = construct_sle_fPC(k,n,f)

g_part = sle_fPC$f
g_hom = solve_hom(sle_fPC)

c = 8/5
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

test_all(k,n,f,g)
```

##### Example 3.17 (Note: Finding such an example with only N = 13 forecasts required a lot of searching...)

```{r}
load("forecasts13.RData")
f = forecasts
k = nrow(f) # 3
n = sum(f[,1]) # 10

sle_fCC = construct_sle_fCC(k,n,f)

g_part = sle_fCC$f
g_hom = solve_hom(sle_fCC)

c = 0.14
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)

test_all(k,n,f,g)
```


