---
title: "Illustrative example"
output: 
  github_document: default
  html_document: default
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding,
  output_format = "all") })
---

We start by loading the functions implementing example generation, linear constraints and some visualizations (and some packages required by the functions).

```{r, message=FALSE}
source("functions.R")
```

As in Appendix B of the manuscript, we use Example 2.4 (b) from Gneiting and Resin (2023) to illustrate some of the workings of these functions.

We start by fixing the number of classes $k$ and the denominator $n$ to generate the forecast probabilities. Note that *all* probabilities are represented as multiples of $1/n$ in what follows.

```{r}
k = 3 # number of classes
n = 4 # common denominator of all forecast probabilities

f = generate_forecasts(k,n)
f
```
Here, each *column* represents a predictive pmf, i.e.,
\[
  \texttt{f[i,j]} = f_j(i).
\]
We assume throughout that forecasts are equiprobable ($p_j = 1/N$).
We now construct the systems of linear equations encoding particular notions of calibration such as marginal or probabilistic calibration. We can combine them and test, whether the particular solution, $\texttt{sle\$f}$, in fact satisfies the system.

```{r}
sle_MC = construct_sle_MC(k,n,f)
sle_PC = construct_sle_PC(k,n,f)

test_sle(sle_MC)
test_sle(sle_PC)

sle = combine_sle(sle_MC,sle_PC)

test_sle(sle)

sle
```
Note that each system also contains the constraints that ensure that probabilities sum to one (equations 1--3 and 7--9) and the linear equations for the particular notions have been multiplied by $1/p_j = N$.

We compute the homogeneous solution to the linear system and use this to construct any other particular solution.

```{r}
g_part = sle$f
g_hom = solve_hom(sle)

c = -0.6 # in [-1,1] for (multiples of) probabilities
g = matrix(g_part + g_hom %*% c,nrow = k,byrow = TRUE)
g
```
Thus, we recovered Example 2.4 (b) from Gneiting and Resin (2023).

```{r}
fractions(cbind(t(f)/n,t(g)/n))
```
We can verify/falsify other notions by constructing the corresponding linear systems and testing whether these are satisfied by the solution $\texttt{g}$.

The example is CEP calibrated (CC) but not fully CEP calibrated (fCC):

```{r}
sle_CC = construct_sle_CC(k,n,f)
test_sle(sle_CC,g)

sle_fCC = construct_sle_fCC(k,n,f)
test_sle(sle_fCC,g)
```

The example is threshold calibrated (TC) but not fully threshold calibrated (fTC):

```{r}
sle_TC = construct_sle_TC(k,n,f)
test_sle(sle_TC,g)

sle_fTC = construct_sle_fTC(k,n,f)
test_sle(sle_fTC,g)
```

The example is not average probabilistically calibrated (aPC):

```{r}
sle_aPC = construct_sle_aPC(k,n,f)
test_sle(sle_aPC,g)
```

The example is not class-wise calibrated (CwC):

```{r}
sle_CwC = construct_sle_CwC(k,n,f)
test_sle(sle_CwC,g)
```

A quick simultaneous assessment of all implemented notions from Table 4 can be run via:

```{r}
test_all(k,n,f,g)
```

To assess quantile calibration, we plot conditional coverages and predictive quantiles:

```{r}
plot_QC(k,n,f,g)
```